---
title: Download wind
editor: source
description: https://raphaelnussbaumer.com/GeoPressureManual/geopressuretemplate-wind.html
---

This script will help you download the wind data for a `tag` and define the movement model.



```{r setup}
id <- "CV019"

knitr::opts_knit$set(root.dir = here::here())
library(GeoPressureR)
library(job)
```

## Set Copernicus credentials

::: callout-caution
*Delete this block when you have read!* 

1. If you don't yet have one, create a ECMWF account at <https://www.ecmwf.int/>. 

2. Accept the licence agreement on [ https://cds.climate.copernicus.eu/datasets/reanalysis-era5-pressure-levels?tab=download#manage-licences] going on the "Licences" tab and select the "Licence to use Copernicus Products".

3. Retrieve your API Token on <https://cds.climate.copernicus.eu/profile>.

4. Saves the token to your local keychain with `ecmwfr` (which calls the API Token `key`) :

```{r}
ecmwfr::wf_set_key("72144268-e78b-4232-9797-4afad84b7860")
```

For more information visit [the ecmwfr documentation](https://bluegreen-labs.github.io/ecmwfr/).
:::

## Create tag

Make sure you have already created the label file with the "1-label.qmd" script.

```{r, cache = TRUE, message=FALSE}
tag <- geopressuretemplate_tag(id, quiet = F)
```

## Download wind data

The [job package](https://lindeloev.github.io/job) allows to download the wind data in the background and let your R console free to use.

```{r, eval = FALSE}
job({
  tag_download_wind(tag)
})
```

Check requests at <https://cds.climate.copernicus.eu/requests>

## Define movement model

### Add wind data

```{r}
graph <- graph_create(
  tag,
  thr_likelihood = config::get("graph_create", id)$thr_likelihood,
  thr_gs = config::get("graph_create", id)$thr_gs
)
```

```{r}
graph <- graph_add_wind(
  graph,
  pressure = tag$pressure,
  thr_as = config::get("graph_add_wind", id)$thr_as
)
```

### Set movement model

Check that the movement model defined in `config.yml` is adequate.

```{r}
graph <- graph_set_movement(graph,
  bird = bird_create(config::get("bird_create", id)$scientific_name)
)
```

Check the movement model

```{r}
plot_graph_movement(graph)
```

Mapping using the graphs

```{r}
#Most Likely Path
path_most_likely <- graph_most_likely(graph, quiet = TRUE)
#kable(head(path_most_likely, 11))
plot_path(path_most_likely)

#Marginal path
marginal <- graph_marginal(graph, quiet = TRUE)
plot(marginal, path = path_most_likely)

#Simulated Paths
path_simulation <- graph_simulation(graph,
  nj = 10, # Number of simulation
  quiet = TRUE
)
plot_path(path_simulation, plot_leaflet = FALSE)

#GeoPressureViz
geopressureviz("CV019")

```
Save data
```{r}
save(tag,
  graph, # format(object.size(graph), units = "MB")
  path_most_likely,
  path_simulation,
  marginal,
  file = "./data/interim/CV019.RData"
)
```

